The Evolution of Phenotypically Invariant Genetic Networks

### 2017-02-06 kalman_walk.tex
added citation for minimal realization proof.

\documentclass[11 pt]{article}
\usepackage{amsmath, amssymb, color, xcolor}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage[backref, hidelinks, colorlinks=true, citecolor=blue!60!black!100]{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, shapes}
\usepackage{caption, subcaption}
\usepackage{natbib} % gives us \citet: Author (year) and \citep: (Author; year)
\usepackage{authblk}

@@

    \item \emph{(josh)} Add biology to introduction. (keep an eye out for concrete numbers we can use!)

@@

    \item \emph{(josh,peter)} Prove or find citation for uniqueness of minimal system up to basis change.

>>>>

\documentclass[11 pt]{article}
\usepackage{amsmath, amssymb, color, xcolor}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage[backref=page, hidelinks, colorlinks=true, citecolor=blue!60!black!100]{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, shapes}
\usepackage{caption, subcaption}
\usepackage{natbib} % gives us \citet: Author (year) and \citep: (Author; year)
\usepackage{authblk}

@@

  \item \emph{(josh)} Add biology to introduction. (keep an eye out for concrete numbers we can use!) \jss{added some relevant biology citations to introduction. Still needs a lot of refinement.}

@@

    \item \emph{(josh \jss{\checkmark},peter)} Prove or find citation for uniqueness of minimal system up to basis change. \jss{See \citep[Chapter 10.6, Theorem 6.9: Fundamental Theorem of Linear Realization Theory.]{kalman1969topics}}
